\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel Space

### 2012-05-18 acknowledgements.tex
some ack

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Save this for last :)

Thanks to Deb Cavlovich, for holding on to this thesis for a few days more for Ben to finish it properly.

Thanks to my advisor, too, I guess, and maybe also to the people I worked with and my friends as well.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{Acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This has been an immensely fun and fulfilling project, and it wouldn't have been possible without the contributions, guidance, and support of many people.

\subsubsection{Big Thanks}

First of all, I owe the lion's share of my gratitude equally to Garth Gibson, Jiri Simsa, and Dave Eckhardt.

Garth's advisorship over the past year has been excellent, from showing me how to keep my research both useful and personally satisfying, to teaching me how to share ideas with fellow researchers, to helping me think through far-off future work directions. Not working directly with his main research groups was sometimes unsettling, but validation was not in short supply: when Garth emailed me unprompted asking for my input on the future of my research field was definitely one of the high points.

Jiri's mentorship was invaluable, both in explanations of complicated algorithms and in general advice on good researcher habits. I would have had a much harder time understanding Dynamic Parial Order Reduction without him, and I suspect my posters and talks would have been much less put-together as well.

Working with Dave to share my project with 15-410 really made the thesis come together. I knew I would have a rough time making Landslide available to 15-410 without compromising the class's integrity policies, and Dave helped me make it work. Dave's advice was also crucial when designing the lecture I gave to 15-410 to explain Landslide and recruit students for the user study; I learned more about lecture design during those two weeks than I ever thought there was to know.

\subsubsection{Landslide's Users}

I'm also highly grateful for all the patient work put in by the kernel programmers who used Landslide.

- user study folks, and TAs, esp nwf, also jboning acrichto rpearl

\subsubsection{Support}

- deb and cathy

- revisers and support - carlo, wolf, sully, joshua, maurer, ghanners

\subsubsection{Collaboration}

A big thanks to Wind River for Simics, the simulation software for which Landslide is built. While developing code to fit into larger infrastructure always has its hairy points, Simics's interfaces were generally pleasant, and the expressive power of operating in its simulation environment was invaluable.

@@

I hope you enjoy reading some or all of this.
